Maybe Slipstreams

### 2014-03-14 paper.tex
Working on the intro some more

@@

\section{Introduction}
\subsection{What is FRP}
Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on time varying values.

\subsection{Why use FRP}
FRP is a useful approach to user interface design because it is declaritive. Most interface design forces you to define exactly how to generate each value. With the time varying values supplied by an FRP network the programmer can choose \textit{what} an interface element is rather than how it is generated. By comosing these values together a higher-level description of what each

>>>>

\addtolength{\topmargin}{-0.5in}

@@

\section{Introduction}
\subsection{What is FRP}
Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on time varying values. The fundamental idea behind it is to allow the programmer to express than ``what'' of a program, and the ``how'' of the program be infered. FRP operates by a series of \textit{behaviors}, which are time varying values that react with one another to form a program.

\subsection{Why use FRP}
FRP is a useful approach to user interface design because it is declarative. Most interface design forces you to define exactly how to generate each value and once the value is generated. The common approach leads to extremly messy interface code. With the time varying values supplied by an FRP network the programmer can choose \textit{what} an interface element is rather than how it is generated. By comosing these values together a higher-level description of what each interface element should be. From this declarative structure the relationship between pieces of the interface implicitly emerges, freeing the programmer from having to tediously define exactly how each relationship is enacted.
